Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2017-01-25 WRITEUP/ms_arxiv/ms.tex
fingers messing around?\!
updated to Karl G Jansky

\subsection{VLA (Archival)}
Our analysis also uses archival data of the 4.885\,GHz
radio continuum obtained with the
VLA (Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

>>>>

\subsection{Karl G. Jansky Very Large Array (Archival)}
Our analysis also uses archival data of the 4.885\,GHz
radio continuum obtained with the
Karl G. Jansky Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.
